babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-09 article.tex
Show bibliography once
No listing captions

% Style of listings
% From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
\usepackage{fancyvrb} 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
  language=R,% set programming language
  basicstyle=\ttfamily\small,% basic font style
  commentstyle=\color{gray},% comment style
  numbers=left,% display line numbers on the left side
  numberstyle=\scriptsize,% use small line numbers
  numbersep=10pt,% space between line numbers and code
  tabsize=2,% sizes of tabs
  showstringspaces=false,% do not replace spaces in strings by a certain character
  captionpos=b,% positioning of the caption below
  breaklines=true,% automatic line breaking
  escapeinside={(*}{*)},% escaping to LaTeX
  fancyvrb=true,% verbatim code is typset by listings
  extendedchars=false,% prohibit extended chars (chars of codes 128--255)
  alsoletter={.<-},% becomes a letter
  alsoother={$},% becomes other
  otherkeywords={!=, ~, $, \&, \%/\%, \%*\%, \%\%, <-, <<-, /},% other keywords
  deletekeywords={c}% remove keywords 
}
\lstset{style=mystyle}

@@

\begin{lstlisting}[language=R, caption=Loading, label=lst:loading_babette, floatplacement=H]
library(babette)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Simplest example, label=lst:simplest_example, floatplacement=H]
out <- run_beast2(
  "alignment.fas"
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  site_models = create_hky_site_model(),
  clock_models = create_rln_clock_model(),
  tree_priors = create_bd_tree_prior()
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Two alignments, label=lst:two_alignments, floatplacement=H]
out <- run_beast2(
  c("anthus_aco.fas", "anthus_nd2.fas"),
  site_models = list(
    create_tn93_site_model(), 
    create_gtr_site_model()
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Example with Yule tree prior with different birth rate distribution, label=lst:diff_distr, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  tree_priors = create_yule_tree_prior(
    birth_rate_distr = create_exp_distr()    
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  posterior_crown_age = 15
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Calculate ESSes, label=lst:calc_esses, floatplacement=H]
traces <- remove_burn_ins(traces = out$estimates, burn_in_fraction = 0.1)
esses <- calc_esses(traces, sample_interval = 1000)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Calculate all summary statistics, label=lst:calc_sum_stats, floatplacement=H]
sum_stats <- calc_sum_stats(
  out$estimates$birthRate, 
  sample_interval = 1000, 
  burn_in_fraction = 0.1
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Show posterior phylogenies, label=lst:densitree, floatplacement=H]
densitree(out$anthus_aco_trees)
\end{lstlisting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{article}

\begin{thebibliography}{}

\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Style of listings
% From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
\usepackage{fancyvrb} 
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
  language=R,% set programming language
  basicstyle=\ttfamily\small,% basic font style
  commentstyle=\color{gray},% comment style
  % numbers=left,% display line numbers on the left side
  numberstyle=\scriptsize,% use small line numbers
  numbersep=10pt,% space between line numbers and code
  tabsize=2,% sizes of tabs
  showstringspaces=false,% do not replace spaces in strings by a certain character
  captionpos=b,% positioning of the caption below
  breaklines=true,% automatic line breaking
  escapeinside={(*}{*)},% escaping to LaTeX
  fancyvrb=true,% verbatim code is typset by listings
  extendedchars=false,% prohibit extended chars (chars of codes 128--255)
  alsoletter={.<-},% becomes a letter
  alsoother={$},% becomes other
  otherkeywords={!=, ~, $, \&, \%/\%, \%*\%, \%\%, <-, <<-, /},% other keywords
  deletekeywords={c}% remove keywords 
}
\lstset{style=mystyle}

@@

\begin{lstlisting}[language=R, floatplacement=H]
library(babette)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2("alignment.fas")
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  site_models = create_hky_site_model(),
  clock_models = create_rln_clock_model(),
  tree_priors = create_bd_tree_prior()
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  c("anthus_aco.fas", "anthus_nd2.fas"),
  site_models = list(
    create_tn93_site_model(), 
    create_gtr_site_model()
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  tree_priors = create_yule_tree_prior(
    birth_rate_distr = create_exp_distr()    
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
out <- run_beast2(
  "alignment.fas",
  posterior_crown_age = 15
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
traces <- remove_burn_ins(traces = out$estimates, burn_in_fraction = 0.1)
esses <- calc_esses(traces, sample_interval = 1000)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
sum_stats <- calc_sum_stats(
  out$estimates$birthRate, 
  sample_interval = 1000, 
  burn_in_fraction = 0.1
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=H]
densitree(out$anthus_aco_trees)
\end{lstlisting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
